Integrated multi-omics analysis reveals Lactobacillus anti-inflammatory process in vaginal tissue

### 2020-12-17 reports/rmarkdown/manuscript/manuscript_template.Rmd
adds figure1 in manuscript

```{r, echo = FALSE, eval = TRUE , fig.asp=6/10}
# Define Layout and set labels
layout(matrix(c(1,1,1,1,      3,3,3,3,          4,4,4,4,
                2,2,2,2,      3,3,3,3,          5,5,5,5,
                6,6,6,6,      9,9,9,9,          9,9,9,9,
                7,7,7,7,     10,10,10,10,     10,10,10,10,
                8,8,8,8,     10,10,10,10,     10,10,10,10 ) , ncol= 12,byrow = T),
       widths = 1,heights = c(1,1,0.5,0.5,0.5))
# layout.show(29)
figlabels <- letters

@@

###################################
# BACTERIAL VAGINOSIS COMPARISSON #
###################################
par(mar=c(1,1,1,1))

@@

###################################
# BACTERIAL VAGINOSIS COMPARISSON #
###################################
par(mar=c(4,4,1,1))
temp <- t(t(2^x-1)/colSums(2^x-1))
taxa <- read.csv2("../../../results/taxonomy.csv",row.names = 1,stringsAsFactors = F,as.is = T)
taxa[is.na(taxa)] <- "NA"
taxa <- taxa[rownames(temp),]
temp <- rowsum(temp , taxa$Class)
o <- order( rowSums(temp) , decreasing = F)
sample_o <- order( as.numeric(metadata$group_M4_CVLv3)+(shann/max(shann)/2) )
temp <- temp[o,sample_o]*100
barplot( temp, las=2 , border = NA , yaxs="i", xaxs="i", col = pal[factor(rownames(temp))] )

>>>>

```{r, echo = FALSE, eval = TRUE , fig.asp=9/10}
# Define Layout and set labels
layout(matrix(c(1,1,1,1,      3,3,3,3,          4,4,4,4,
                2,2,2,2,      3,3,3,3,          5,5,5,5,
                6,6,6,6,      9,9,9,9,          9,9,9,9,
                7,7,7,7,     10,10,10,10,     10,10,10,10,
                8,8,8,8,     10,10,10,10,     10,10,10,10 ) , ncol= 12,byrow = T),
       widths = 1,heights = c(1,1,.7,.7,.7))
# layout.show(29)
figlabels <- letters

@@

###################################
# BACTERIAL VAGINOSIS COMPARISSON #
###################################
par(mar=c(1,4,1,10))

@@

###################################
# BACTERIAL VAGINOSIS COMPARISSON #
###################################
par(mar=c(4,4,1,10))
temp <- t(t(2^x-1)/colSums(2^x-1))
taxa <- read.csv2("../../../results/taxonomy.csv",row.names = 1,stringsAsFactors = F,as.is = T)
taxa[is.na(taxa)] <- "NA"
taxa <- taxa[rownames(temp),]
temp <- rowsum(temp , taxa$Class)
temp[is.nan(temp)] <- 0
o <- order( rowSums(temp) , decreasing = T)
sample_o <- order( metadata$joint_clustering )
temp <- temp[o,sample_o]*100
temp <- temp[-grep("NA",rownames(temp)),]
temp <- rbind(temp[1:15,], Other = colSums(temp[16:nrow(temp),]) )

taxa_pal <- c(RColorBrewer::brewer.pal(8,"Pastel2"),RColorBrewer::brewer.pal(8,"Pastel1"))
barplot( temp, las=2 , border = NA , yaxs="i", xaxs="i",
         col = taxa_pal[factor(rownames(temp))] )
legend(x = par("usr")[c(2)],
       y = par("usr")[c(4)],title.adj = 0,
       legend = rownames(temp),xjust = 0,yjust = 1,
       bty = "n",pch = 22,pt.cex = 2,cex = .8,xpd=T,
       pt.bg = taxa_pal)
